%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
\cventry
    {Software Engineer} % Job title
    {Chakra Labs} % Company
    {United States (Remote)} % Location
    {Jan. 2026 – Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Building high-fidelity, pixel-perfect interfaces at extreme speed to create complex training environments for computer-use agents.}
        \item {Hooking up environment states to the Dojo engine using \texttt{useDojoState} to facilitate real-time Reinforcement Learning feedback loops.}
        \item {Shipping stateful, interactive UIs for AI research in record time, maintaining a relentless delivery pace in a high-growth startup environment.}
      \end{cvitems}
    }
%---------------------------------------------------------
\cventry
    {Forward Deployed Engineer} % Job title
    {Lyra} % Company
    {Sydney, Australia (Remote)} % Location
    {Dec. 2025 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Shipping production-grade software for high-growth companies including Microsoft, Elsa, and YC-backed startups such as Paraform and Credal.}
        \item {Bridging the gap between product engineering and client requirements to deliver customized solutions and ensure seamless platform integration.}
        \item {Driving end-to-end feature development and deployment, contributing to the growth and technical success of partner organizations.}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Agent Evaluator} % Job title
    {Composer} % Company
    {United States (Remote)} % Location
    {Dec. 2025 - Jan. 2026} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led the benchmarking of Browser Use Agent Architecture on two major web agent benchmarks, successfully achieving the \#1 rank on both.}
        \item {Developed systematic evaluation frameworks to identify edge cases in LLM-generated outputs, providing critical feedback for prompt optimization and model fine-tuning.}
        \item {Performed rigorous software testing and benchmarking to ensure the robustness and reliability of autonomous agent behaviors.}
      \end{cvitems}
    }
    
\cventry
    {Full-Stack Engineer} % Job title
    {insightfactory.ai} % Company
    {Adelaide, Australia} % Location
    {May. 2025 - Dec. 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led the architectural design and development of production features across the platform using .NET, C\#, React, TypeScript, and SQL Server, ensuring scalability, maintainability, and clear system boundaries.}
        \item {Owned end-to-end feature delivery, from requirement engineering and technical scoping to implementation, testing, and deployment, improving team delivery velocity and code quality.}
        \item {Designed and implemented core business logic workflows, contributing to high-impact product modules and collaborating with cross-functional teams to align technical decisions with business needs.}
      \end{cvitems}
    }
%---------------------------------------------------------
\cventry
    {Software Engineer Intern} % Job title
    {Aubot} % Company
    {Melbourne, Australia (Remote)} % Location
    {Nov. 2024 - Mar. 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed backend features for the Aubot Academy platform using Django, optimizing database query efficiency to improve latency by 10ms and boost real-time responsiveness for over 150 active students.}
        \item {Assessed, curated, and ported over 520 programming exercises in algorithms, data structures, Advanced  Python and Java onto the platform, enhancing the learning resources for over 8,900 students on Aubot Academy.}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Research Assistant} % Job title
    {Australian Institute for Machine Learning} % Company
    {Adelaide, Australia} % Location
    {Nov. 2024 - Mar.2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Leveraged Meta Aria Glass and Repaper devices for data collection, contributing critical datasets for training touch interaction models and successfully identified useful data from the devices by reading documentation and SDKs.}
        \item {Designed and proposed a novel synchronization method, utilizing Python and custom algorithms, achieving an average latency reduction of 100ms between devices.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
